Test data

### 2022-07-20 Shiny/Test/Test data.Rmd
Stylering.

read_proff7 <- function(file, start, end){
    read_html(file, encoding = "UTF-8") |> 
      html_node("#inner-frame") |> 
      html_table() |> 
      select( # removing empty column
        REGNSKAPSPERIODE:all_of(start)) |> # using all_of()
      mutate( # removing whitespace
        REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
      ) |> 
      filter( # removing duplicate table - no idea why it's necessary
        !row_number() > 176
      ) |>
      filter( # removing duplicate rows
        !grepl("Lukk", REGNSKAPSPERIODE)
      ) |> 
      pivot_longer( # tidying data
        all_of(end):all_of(start), names_to = "year"
        ) |> # using all_of()
      mutate( # changing to real NAs and turning years into numbers
        value = na_if(value, "-"),
        year = as.integer(year)) |> 
      mutate( # adding currency column
        valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
      ) |> 
      fill( # filling the currency column
        valutakode, .direction = "updown"
      ) |> 
      filter( # removing dates and redundant currency
        REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
          REGNSKAPSPERIODE != "Valutakode") |> 
      mutate( # removing whitespace in numbers
        value = str_replace_all(value, "\\s", ""),
        value = as.numeric(value),
        value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value),
        value = value * 1000
      ) |> 
      distinct() |> # removing any remaining duplicate rows
      pivot_wider( # pivoting
        names_from = REGNSKAPSPERIODE, values_from = value
      ) |> 
      clean_names() |> # tidying names
      select(-lederlonn_i_hele_1000,
             -resultatregnskap_i_hele_1000,
             -balanseregnskap_i_hele_1000) |> # removing headings
      rename( # making it clear what lonn refers to
        lederlonn = lonn
      ) |> 
      arrange(desc(year)) # arranging by year
}

@@

@@

# Original
kreft_html |> 
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |> 
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |> 
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = ifelse(length(unique(kreft_html$valutakode)) == 1,
                    label_dollar(prefix = str_c(kreft_html$valutakode[1], " ")),
                    label_dollar(prefix = "? "))
      ) +
  scale_fill_met_d("Troy") +
  labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
       subtitle = ifelse(length(unique(kreft_html$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))

>>>>

read_proff7 <- function(file, start, end) {
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |>
    select( # removing empty column
      REGNSKAPSPERIODE:all_of(start)
    ) |> # using all_of()
    mutate( # removing whitespace
      REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
    ) |>
    filter( # removing duplicate table - no idea why it's necessary
      !row_number() > 176
    ) |>
    filter( # removing duplicate rows
      !grepl("Lukk", REGNSKAPSPERIODE)
    ) |>
    pivot_longer( # tidying data
      all_of(end):all_of(start),
      names_to = "year"
    ) |> # using all_of()
    mutate( # changing to real NAs and turning years into numbers
      value = na_if(value, "-"),
      year = as.integer(year)
    ) |>
    mutate( # adding currency column
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |>
    fill( # filling the currency column
      valutakode,
      .direction = "updown"
    ) |>
    filter( # removing dates and redundant currency
      REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
        REGNSKAPSPERIODE != "Valutakode"
    ) |>
    mutate( # removing whitespace in numbers
      value = str_replace_all(value, "\\s", ""),
      value = as.numeric(value),
      value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value),
      value = value * 1000
    ) |>
    distinct() |> # removing any remaining duplicate rows
    pivot_wider( # pivoting
      names_from = REGNSKAPSPERIODE, values_from = value
    ) |>
    clean_names() |> # tidying names
    select(
      -lederlonn_i_hele_1000,
      -resultatregnskap_i_hele_1000,
      -balanseregnskap_i_hele_1000
    ) |> # removing headings
    rename( # making it clear what lonn refers to
      lederlonn = lonn
    ) |>
    arrange(desc(year)) # arranging by year
}

@@

read_proff_tidied <- function(file, start, end) {
    read_html(file, encoding = "UTF-8") |>
        html_node("#inner-frame") |>
        html_table() |>
        # removing empty column
    select(REGNSKAPSPERIODE:all_of(start)) |>
        # removing whitespace
    mutate(REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)) |>
        # removing duplicate table - no idea why it's necessary
    filter(!row_number() > 176) |>
        # removing duplicate rows
    filter(!grepl("Lukk", REGNSKAPSPERIODE)) |>
        # tidying data
    pivot_longer(
        all_of(end):all_of(start),
        names_to = "year"
    ) |>
        # changing to real NAs and turning years into numbers picking
        # out the currency
    mutate(
        value = na_if(value, "-"),
        year = as.integer(year),
        valutakode = ifelse(
            REGNSKAPSPERIODE == "Valutakode", value,
            NA
        )
    ) |>
        # filling the currency column
    fill(valutakode, .direction = "updown") |>
        # removing dates and redundant currency
    filter(
        REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE !=
            "Startdato" & REGNSKAPSPERIODE != "Valutakode"
    ) |>
        # removing white space in numbers and removing years as numbers
    mutate(
        value = str_replace_all(value, "\\s", ""),
        value = as.numeric(value),
        value = ifelse(
            grepl("i hele 1000", REGNSKAPSPERIODE),
            NA, value
        )
    ) |>
        # removing any remaining duplicate rows
    distinct() |>
        # pivoting
    pivot_wider(names_from = REGNSKAPSPERIODE, values_from = value) |>
        # tidying names
    clean_names() |>
        # removing headings
    select(
        -lederlonn_i_hele_1000, -resultatregnskap_i_hele_1000,
        -balanseregnskap_i_hele_1000
    ) |>
        # making it clear what lonn refers to
    rename(lederlonn = lonn) |>
        # Creating new variables for plots
    mutate(
        annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
        balance_positive = ifelse(
            sum_egenkapital_og_gjeld >= 0, TRUE,
            FALSE
        )
    ) |>
        # arranging by year
    arrange(desc(year))
}

@@

# Original
kreft_html |>
  select(
    year, lederlonn, leder_annen_godtgjorelse
  ) |>
  rename(
    Year = year,
    Salary = lederlonn,
    `Other compensation` = leder_annen_godtgjorelse
  ) |>
  pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
  ggplot(aes(Year, value, fill = Compensation)) +
  geom_col() +
  scale_y_continuous(
    labels = ifelse(length(unique(kreft_html$valutakode)) == 1,
      label_dollar(prefix = str_c(kreft_html$valutakode[1], " ")),
      label_dollar(prefix = "? ")
    )
  ) +
  scale_fill_met_d("Troy") +
  labs(
    x = "Year", y = "Total compensation", title = "Annual CEO compensation",
    subtitle = ifelse(length(unique(kreft_html$valutakode)) == 1,
      "",
      "Note: not all values are denominated in the same currency"
    )
  )
